---
title: "Upcoming events with contributions from the working group"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    highlight: pygments
    number_sections: yes
    self_contained: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r setup, include = FALSE, echo = FALSE}
## load packages
packs.html <- c("knitr", "pander", "reporttools", "dplyr", "readxl")
for (i in 1:length(packs.html)){library(packs.html[i], character.only = TRUE)}

knitr::opts_chunk$set(echo = TRUE)

## talks
path <- getwd()
talks <- as.data.frame(read_excel(paste(path, "/data/seminars.xlsx", sep = ""), col_types = NULL))

# prepare date strings
d <- substr(talks$date, 1, 2)
m <- substr(talks$date, 4, 5)
y <- substr(talks$date, 7, 11)

rdate <- paste(y, m, d, sep = "")
talks$rdate <- rdate

# select talks with past date
talks <- (talks %>% filter(rdate > gsub("-", "", as.character(Sys.Date()))) %>% filter(!is.na(date)))

talks <- (talks %>% group_by(rdate, talknr)  %>% 
        arrange(
            rdate, 
            talknr
        ))
talks <- as.data.frame(talks)
rdate <- unique(talks$rdate)
dates <- unique(select(talks, date))[, 1]
```

## PSI Webinar: Applying the Estimand Framework to Clinical Pharmacology Trials with a Case Study in Bioequivalance

**Link and Details:**

<https://psiweb.org/events/event-item/2025/06/03/default-calendar/psi-webinar-applying-the-estimand-framework-to-clinical-pharmacology-trials-with-a-case-study-in-bioequivalance>

**Date:** Tuesday 3rd June 2025 <br>
**Time:** 14:00 - 15:15 BST <br>
**Location:** Online via Zoom

This webinar is free to attend. To register for this event, please [click here](https://psi.glueup.com/event/139872/)

**Overview:** 
Are you involved in designing or writing clinical pharmacology protocols? Then don't miss this webinar! We'll focus on the core concepts of estimands, specifically aimed at clinical trial development teams – no heavy statistical jargon required.

Join the expert authors of a recent paper [1] as they introduce the game-changing concepts of the “estimand framework” [2], "intercurrent events" [2], and the estimand thinking process. In this beginner-friendly session, you'll learn, step-by-step, how to apply estimand thinking to your trials, leading to clearer objectives and more meaningful results.

We'll dive into a practical case study – a bioequivalence trial – to illustrate how the estimand framework can eliminate ambiguity and bring greater transparency to the key clinical questions you're investigating. Beyond this specific example, we'll discuss the broader impact of estimands on various clinical pharmacology trials.

Come ready to learn and ask questions! The presenters will be joined by some of their co-authors for an interactive Q&A session after the presentation.

[1] [Applying the estimand framework to clinical pharmacology trials with a case study in bioequivalence - Lynggaard - 2025 - British Journal of Clinical Pharmacology - Wiley Online Library](https://urldefense.com/v3/__https:/bpspubs.onlinelibrary.wiley.com/doi/10.1111/bcp.16347__;!!H9nueQsQ!-BVxTMLZb4QPW8zBOvA8OeoZROIXtwcRtkoba6s_XMrHnKfVJegMZHrE3D2tpc9SX7PcSdzs4L6l4uWUpczhVO5OMGA$)

[2] International Council for Harmonisation of Technical Requirements for Pharmaceuticals for Human Use. Addendum on Estimands and Sensitivity Analysis in Clinical Trials to the Guideline on Statistical Principles for Clinical Trials E9(R1). <https://database.ich.org/sites/default/files/E9-R1_Step4_Guideline_2019_1203.pdf>. Published November 2019

<!-- Below a list of further upcoming events with contributions of the WG.-->

```{r echo = FALSE, message = FALSE, warning = FALSE, include = FALSE}
if (length(dates) > 0) {
# how to do this with child documents: https://gist.github.com/rmoff/a043676a2f084b81a434

out1 <- NULL
for (i in 1:length(dates)){
  out1 <- c(out1, knit_expand('tools/seminars1.Rmd'))
}

# the "knit" command somehow produces unwanted output, this is why I assign its output to a and use a separate chunk to display a
a <- knit(text = unlist(paste(out1, collapse = '\n')), quiet = TRUE)
}
```

```{r conferences, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
if (length(dates) > 0) {
  cat(a)
}
```
