---
title: "Upcoming events with contributions from the working group"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    highlight: pygments
    number_sections: yes
    self_contained: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r setup, include = FALSE, echo = FALSE}
## load packages
packs.html <- c("knitr", "pander", "reporttools", "dplyr", "readxl")
for (i in 1:length(packs.html)){library(packs.html[i], character.only = TRUE)}

knitr::opts_chunk$set(echo = TRUE)

## talks
path <- getwd()
talks <- as.data.frame(read_excel(paste(path, "/data/seminars.xlsx", sep = ""), col_types = NULL))

# prepare date strings
d <- substr(talks$date, 1, 2)
m <- substr(talks$date, 4, 5)
y <- substr(talks$date, 7, 11)

rdate <- paste(y, m, d, sep = "")
talks$rdate <- rdate

# select talks with past date
talks <- (talks %>% filter(rdate > gsub("-", "", as.character(Sys.Date()))) %>% filter(!is.na(date)))

talks <- (talks %>% group_by(rdate, talknr)  %>% 
        arrange(
            rdate, 
            talknr
        ))
talks <- as.data.frame(talks)
rdate <- unique(talks$rdate)
dates <- unique(select(talks, date))[, 1]
```

## PSI Webinar: Enhancing Clinical Study Reporting with the Estimand Framework

**Link and Details:**

<https://psi.glueup.com/event/172627/>

**Date:** Tuesday 21st April2026 <br> **Time:** 14:00 - 15:30 BST <br> **Location:** Online

This webinar is free to attend. To register for this event, please [click here](https://psi.glueup.com/event/172627/register/)

**Target audience:** Clinical researchers, medical writers, statisticians, and anyone engaged in reporting clinical trial results.

**Key Takeaways:**

-   Why estimands matter for decision-making and communication.
-   Practical considerations for integrating estimands into study reports.
-   Lessons learned from case studies and real-world applications.

<!-- Below a list of further upcoming events with contributions of the WG.-->

```{r echo = FALSE, message = FALSE, warning = FALSE, include = FALSE}
if (length(dates) > 0) {
# how to do this with child documents: https://gist.github.com/rmoff/a043676a2f084b81a434

out1 <- NULL
for (i in 1:length(dates)){
  out1 <- c(out1, knit_expand('tools/seminars1.Rmd'))
}

# the "knit" command somehow produces unwanted output, this is why I assign its output to a and use a separate chunk to display a
a <- knit(text = unlist(paste(out1, collapse = '\n')), quiet = TRUE)
}
```

```{r conferences, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
if (length(dates) > 0) {
  cat(a)
}
```
